Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-28 formally.tex
tweaks per publisher requests

A simple auxiliary judgement, $\bar\alpha~\mathsf{movements}$, defined in
the supplement, establishes that $\bar\alpha$ consists only of actions of
the form $\aMove{\delta}$.

@@

\fbox{$\performAna{\hGamma}{\zexp}{\htau}{\bar{\alpha}}{\zexp'}$}
\vspace{-12px}
\begin{subequations}\label{rules:iterated-ana}
\begin{mathpar}
~~~~~~~\inferrule{ }{
  \performAnaI{\hGamma}{\zexp}{\htau}{\cdot}{\zexp}
}
~~~~~~~~~~~~~~
\inferrule{
  \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}\\\\
  \performAnaI{\hGamma}{\zexp'}{\htau}{\bar\alpha}{\zexp''}
}{
  \performAnaI{\hGamma}{\zexp}{\htau}{\alpha; \bar\alpha}{\zexp''}
}
~~~~~~~~~~
\text{(\ref*{rules:iterated-ana}a-b)}
\end{mathpar}
\end{subequations}
\caption{Iterated Action Judgements}
\label{fig:multistep}
\end{figure}

@@

\subsubsection{Construction}\label{sec:construction} The construction
actions, $\aConstruct{\psi}$, are used to construct terms of a shape
indicated by $\psi$ at the cursor.

@@

\paragraph{Variables} The $\aConstruct{\fvar{x}}$ action places the
variable $x$ into an empty hole. If that hole is being asked to synthesize
a type, then the result synthesizes the hypothesized type:
\begin{equation}
  \label{r:conevar}
  \inferrule{ }{
    \performSyn{\hGamma, x : \htau}{\zwsel{\hehole}}{\tehole}{\aConstruct{\fvar{x}}}{\zwsel{x}}{\htau}
  }
\end{equation}
If the hole is being analyzed against a type that is consistent with the
hypothesized type, then the action semantics goes through the {action
  subsumption rule} described in Sec. \ref{sec:action-subsumption}. If the
hole is being analyzed against a type that is inconsistent with the
hypothesized type, $x$ is placed inside a hole:
\begin{equation}
 \label{r:conevar2}
  \inferrule{
    \tincompat{\htau}{\htau'}
  }{
    \performAna{\hGamma, x : \htau'}{\zwsel{\hehole}}{\htau}{\aConstruct{\fvar{x}}}{\hhole{\zwsel{x}}}
  }
\end{equation}
The rule above featured on Line 16 of Figure \ref{fig:second-example}.

>>>>

A simple auxiliary judgement, $\bar\alpha~\mathsf{movements}$ (not shown) establishes that $\bar\alpha$ consists only of actions of
the form $\aMove{\delta}$.

@@

@@

\fbox{$\performAna{\hGamma}{\zexp}{\htau}{\bar{\alpha}}{\zexp'}$}
\vspace{-12px}
\begin{subequations}\label{rules:iterated-ana}
\begin{mathpar}
~~~~~~~\inferrule{ }{
  \performAnaI{\hGamma}{\zexp}{\htau}{\cdot}{\zexp}
}
~~~~~~~~~~~~~~
\inferrule{
  \performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}\\\\
  \performAnaI{\hGamma}{\zexp'}{\htau}{\bar\alpha}{\zexp''}
}{
  \performAnaI{\hGamma}{\zexp}{\htau}{\alpha; \bar\alpha}{\zexp''}
}
~~~~~~~~~~
\text{(\ref*{rules:iterated-ana}a-b)}
\end{mathpar}
\end{subequations}
\caption{Iterated Action Judgements}
\label{fig:multistep}
\end{figure}
\subsubsection{Construction}\label{sec:construction} The construction
actions, $\aConstruct{\psi}$, are used to construct terms of a shape
indicated by $\psi$ at the cursor.

@@

\paragraph{Variables} The $\aConstruct{\fvar{x}}$ action places the
variable $x$ into an empty hole. If that hole is being asked to synthesize
a type, then the result synthesizes the hypothesized type:
\begin{equation}
  \label{r:conevar}
  \inferrule{ }{
    \performSyn{\hGamma, x : \htau}{\zwsel{\hehole}}{\tehole}{\aConstruct{\fvar{x}}}{\zwsel{x}}{\htau}
  }
\end{equation}

If the hole is being analyzed against a type that is consistent with the
hypothesized type, then the action semantics goes through the {action
  subsumption rule} described in Sec. \ref{sec:action-subsumption}. If the
hole is being analyzed against a type that is inconsistent with the
hypothesized type, $x$ is placed inside a hole:
\begin{equation}
 \label{r:conevar2}
  \inferrule{
    \tincompat{\htau}{\htau'}
  }{
    \performAna{\hGamma, x : \htau'}{\zwsel{\hehole}}{\htau}{\aConstruct{\fvar{x}}}{\hhole{\zwsel{x}}}
  }
\end{equation}
The rule above featured on Line 16 of Figure \ref{fig:second-example}.
